---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

First let's load the data.

```{r}
library(knitr)
library(readr)
library(dplyr, quietly=TRUE, warn.conflicts=FALSE)
data <- read_csv('activity.zip')
```



## What is mean total number of steps taken per day?

First let's get the total steps per day.

```{r}
total_steps_by_day <- data %>% group_by(date) %>% summarise(total_steps=sum(steps, na.rm=TRUE), .groups="keep")
```

Now let's examine a histogram of the number of steps per day.


```{r}
hist(total_steps_by_day$total_steps, xlab="Steps per day", ylab="Number of days with the number of steps", main="Histogram of steps taken in a day")
```

Now let's get the mean steps per day.


```{r}
mean(total_steps_by_day$total_steps)
```

Now let's get the median steps per day.



```{r}
median(total_steps_by_day$total_steps)
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
